
\newpage

\setcounter{section}{0}

\begin{center}
	\heiti\zihao{4} Translation
\end{center}

\subsection{Unit 1}
\begin{enumerate}
	\item 众所周知,中国书法是一门独特的艺术,也是世界上独一无二的艺术瑰宝。
	
	As we all know, Chinese calligraphy is a unique art and a one-of-a-kind artistic treasure in the world.
	
	\item 汉字在漫长的演变过程中,始终起着交流思想、传承文化的重要作用。
	
	During its long evolution process, Chinese characters have always played an important role in communicating ideas and inheriting culture.
	
	
	\item 很显然,中国书法的形成、发展与汉字的演变存在着密不可分的关系。
	
	It is obvious that the formation and development of Chinese calligraphy are inextricably linked to the evolution of Chinese characters.
	
\end{enumerate}

\subsection{Unit 2}
\begin{enumerate}
	\item 改革开放以来,中国的教育事业得到了快速发展,并取得了引人瞩目的成就。
	
	Since the reform and opening up, China's education has developed rapidly and achieved remarkable results.
	
	\item 中国的教育成就反映在九年义务教育的全面普及和高等教育大众化的实现等多个方面。
	
	China's educational achievements are reflected in many aspects, such as the universalization of nine-year compulsory education and the realization of mass higher education.
	
	\item 我们将深入实施科教兴国战略,坚持教育优先发展,为党育人、为国育才,全面提高人才自主培养质量。
	
	We will implement the strategy of building a country through science and education, adhere to the priority development of education, educate people for the Party and the country, and comprehensively improve the quality of independent talent training.
	
\end{enumerate}


\subsection{Unit 3}
\begin{enumerate}
	\item 如今,很多年轻人不再只选择稳定的工作,他们更愿意自主创业,依靠自己的智慧和努力去证明他们的自我价值。
	
	Nowadays, many young people no longer choose stable jobs. They prefer to start their own businesses and rely on their own wisdom and hard work to prove their self-worth.
	
	\item 创业者的成功不但会创造财富,增加就业机会,改善大家的生活,而且从长远来看,对于我们的国家也是一件好事。
	
	The success of entrepreneurs will not only create wealth, increase employment opportunities and improve everyone's lives, but in the long run, it will also be a good thing for our country.
	
	\item 中国政府大力鼓励和支持创业和创新,这会进一步激发年轻人的热情,增强他们的信心。
	
	The Chinese government strongly encourages and supports entrepreneurship and innovation, which will further inspire young people's enthusiasm and enhance their confidence.
	
\end{enumerate}



\subsection{Unit 4}
\begin{enumerate}
	\item 丝绸之路是中国古代的交通线路网络,也是中国最早用于国际贸易和文化交流的渠道。
	
	The Silk Road is a network of ancient Chinese transportation routes and the earliest channel used by China for international trade and cultural exchange.
	
	\item 在古代,丝绸之路有效地促进了各国之间经济文化的交流,从而大大推动了世界文明的进程。
	
	In ancient times, the Silk Road effectively promoted economic and cultural exchanges between countries, thus greatly promoting the progress of world civilization.
	
	\item 在新的历史条件下,中国提出了以合作共赢为核心的"一带一路"倡议,得到了沿线各国的积极响应。
	
	Under the new historical conditions, China proposed the "Belt and Road" initiative with win-win cooperation as the core, which received positive responses from countries along the route.
	
\end{enumerate}

\subsection{Unit 5}
\begin{enumerate}
	\item 中庸思想是儒家思想的核心之一,"中"不是折中,而是处理事情时的一种适度的方法。
	
	The idea of ​​moderation is one of the core ideas of Confucianism. "Middle" does not mean compromise, but a moderate way of dealing with things.
	
	\item 孔子主张,应该通过自身修养把中庸思想融入日常行为中,使之成为一种美德。
	
	Confucius advocated that one should integrate the doctrine of the mean into daily behavior through self-cultivation so that it becomes a virtue.
	
	\item 一直以来,中庸思想为民族精神的构建、智慧的传播和文化的发展发挥着不可估量的作用。
	
	The idea of ​​moderation has always played an immeasurable role in the construction of national spirit, the dissemination of wisdom and the development of culture.
	
\end{enumerate}

\subsection{Unit 6}
\begin{enumerate}
	\item 国民幸福指数用以衡量人们的幸福感,还能反映一个国家或地区的经济发展水平和居民生活水平。
	
	The Gross National Happiness Index is used to measure people's happiness and can also reflect the economic development level and living standards of a country or region.
	
	\item 随着中国经济的高速增长,中国政府越来越重视人民群众的生活质量和国民幸福指数。
	
	With the rapid growth of China's economy, the Chinese government has attached increasing importance to the quality of life of the people and the national happiness index.
	
	\item 不断改善人民群众的生活条件,让他们得到更多实惠,将促进国民幸福指数不断提升。
	
	Continuously improving people's living conditions and allowing them to benefit more will promote the continuous improvement of the national happiness index.
	
\end{enumerate}

